\tool: Programmable, Scalable, Efficient Secure Two-Party Computation

### 2017-10-24 OaklandSubmission/intro.tex
intro first part

Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly and efficiently without tool
support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure  computation  accessible to the software developer community.

@@

Secure multi-party computation (\mpc) \cite{yao,gmw} is a powerful
cryptographic tool that allows a set of mutually distrusting parties
to compute a joint function of their secret inputs. Examples of these
include {\em secure prediction} \cite{shafindss,wu,barni,minionn,secureml}. Here,  one party holds the propriety classifier for disease, genomics or spam detection and the other party  
holds the private input and the second party learns the classification label. Since the introduction of
\mpc in 1980's, there has been a long sequence of work that has
transformed \mpc from a mere theoretical tool to something practically
efficient and usable. Hence, there have been efforts to make \mpc
accessible to non-specialist programmers. To understand the
state-of-the-art, let us consider the following 
example that is the sub-computation in many classification tasks.

Suppose a developer wants to compute $w^Tx >b$ securely using
\mpc. With the current techniques, he has three options. \aseem{We should
  use she for the programmer instead of he?}
\begin{tiret}
\item He can code up the functionality in a programmer friendly
  domain-specific language such as
  \cite{lambdaps,wysteria,oblivm,smcl} that would automatically
  compile it to an SMC protocol. The downside is that all of these
  works build on a cryptographic back-end that is either entirely
  boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated \mpc protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations for efficiency.

\item To address this issue of efficient representation, recently Demmler et al. \cite{aby} gave a cryptographic protocol for \mpc where the parties can mix arithmetic and boolean computations.
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of
trade-offs between arithmetic and boolean cryptographic
schemes as well as the complex inter-conversion costs, and manually split the functionality into such parts accordingly. In
their framework, the programmer is required to write circuits
consisting of  arithmetic and boolean gates along with appropriate
conversion gates. In short, as is also mentioned by the authors, the current system of ABY is not suitable
to be used by non-specialist programmers. \divya{since they say in future they want to automate the splitting.}

>>>>

Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptographic protocols
and cannot be expected to implement them correctly and efficiently without tool
support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure  computation  accessible to the software developer community.

@@

Secure two-party computation (\mpc) \cite{yao,gmw} is a powerful
cryptographic tool that allows two mutually distrusting parties
to compute a joint function of their secret inputs such as {\em secure prediction} \cite{shafindss,wu,barni,minionn,secureml}. Here,  one party holds the propriety classifier for disease, genomics or spam detection and the other party  
holds the private input and the second party learns the classification label such as the presence of the disease. Since its introduction
\mpc in 1980's, there has been a long sequence of work that has
transformed \mpc from a mere theoretical tool to something practically
efficient and usable. Hence, there have been efforts to make \mpc
accessible to non-specialist programmers. To understand the
state-of-the-art, let us consider the following 
example that is the sub-computation in many classification tasks.

Suppose a developer wants to compute $w^Tx >b$ securely using
\mpc, where $w$ and $x$ are two vectors, $b$ is a scalar, and $w^Tx$ denotes the inner product of $w$ and $x$.  With the current techniques, he has three options. \aseem{We should
  use she for the programmer instead of he?}
\begin{tiret}
\item He can code up the functionality in a programmer friendly
  domain-specific language such as
  \cite{lambdaps,wysteria,oblivm,smcl,cbmcgc} that would automatically
  compile it to a \mpc protocol. The downside is that all of these
  works build on a cryptographic back-end that takes as input a functionality expressed as either a boolean circuit \cite{yao,gmw} or an arithmetic circuit \cite{homo}.
  The efficiency of the generated \mpc protocol is hence, bounded by the possibility of efficiently representing the functionality in one of these circuit representations. For instance, multiplication of two $\ell$-bit integers can be expressed as a boolean circuit of size  $O(\ell^2)$ or an arithmetic circuit with 1 multiplication gate. 
Hence, for better efficiency, we would like to securely compute $w^Tx$ using an arithmetic circuit and the comparison with $b$ using a boolean circuit. \divya{that is not supported by above systems.}
In fact, most interesting functions require a mix of arithmetic and boolean computations for efficiency.

\item To address this issue of efficient representation, recently Demmler et al. \cite{aby} gave a cryptographic protocol for \mpc where the functionality can be expressed as a circuit with a mix of both arithmetic and boolean parts.
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, in their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate
inter-conversion gates.
This requires the programmer to be aware of
trade-offs between arithmetic and boolean cryptographic
schemes as well as the complex inter-conversion costs between arithmetic and boolean, and manually split the functionality into such parts accordingly.  
In short, as is also mentioned by Demmler et al., the current system  is not suitable
to be used by \divya{non-cryptography expert developers. }
